Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-05 paper.tex
Description of "Node-Link" representations

OD type representations are frequently used when the origin and destination preside over intermediate locations on the path of movement. 
The OD Matrix is most common visualization technique in this type of representation. 
Rows and columns correspond to locations while cells are coloured to express the volume of flow.

>>>>

OD type representations are frequently used when the origin and destination preside over intermediate locations on the path of movement. 
The OD Matrix is most common visualization technique in this type of representation. 
Rows and columns correspond to locations while cells are coloured to express the volume of flow.
OD matrices can be reordered to emphasise connectivity between locations.
While this feature is particularly useful for identifying trends in the data, the tabular display is challenging for lay users to interpret and  less expressive of connections between locations than representations based on the node-link metaphor.
